Market simulator

### 2020-10-05 analysis/05_market_simulator.Rmd
New tab to render imported data to make sure it worked.
Comments about next steps

```{r organization-reactive-table}
# Placeholder for organization reactive table
org_table <- as.data.frame(matrix(0, nrow = nrow(organization_data)))

@@

@@

>>>>

```{r organization-reactive-table}
# Placeholder for organization reactive table
org_table <- as.data.frame(matrix(0, nrow = nrow(organization_data)))
# org_table <- reactive({read.csv(input$file_org$datapath)})

@@

# I think what we need to do to import data to fill this reactive element we need it look something like this

# org_table$org1_value[where (input$file_org == 1) and the corresponding level matches %in% org_table$levels] <- 1

@@

### Imports

```{r import}
# Render the organization configurations as a table
renderTable({
  org_import = read.csv(input$file_org$datapath)

  org_import
})

# Render the persona configurations as a table
renderTable({
  per_import = read.csv(input$file_per$datapath)

  per_import
})
